### 2021-08-05 paper/paper.tex
added gingerbread man example figures and reproducibility instructions

Some of the main features of \trixi are demonstrated in the following figures.
Figure~\ref{fig:kelvin_helmholtzs} demonstrates entropy-dissipative shock-capturing
methods with adaptive mesh refinement applied to a classical Kelvin-Helmholtz
flow instability problem.

@@

\todo{TODO: Andrew, add gingerbread man example for acoustics} %TODO: Andrew

@@

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-Euler}
\end{figure}

@@

>>>>

Some of the main features of \trixi are demonstrated in the following figures.
Figure~\ref{fig:kelvin_helmholtzs} demonstrates entropy-dissipative shock-capturing
methods with adaptive mesh refinement applied to a classical Kelvin-Helmholtz
flow instability problem. Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equation~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh in
Figure~\ref{fig:pressure_waves}(d) was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.

@@

\begin{figure}[htbp]
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_00}
    \caption{Pressure at time $t = 0$.}
  \end{subfigure}%
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_08}
    \caption{Pressure at time $t = 8$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_16}
    \caption{Pressure at time $t = 16$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_mesh}
    \caption{Unstructured quad mesh.}
  \end{subfigure}%
  \caption{Numerical solutions of pressure wave scattering for the acoustic 
                perturbation equations at three times as well as the unstructured, 
                curvilinear quadrilateral mesh.}
  \label{fig:pressure_waves}
\end{figure}

@@

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}

@@

\todo{TODO: Plot of this comparison with the \lstinline{TreeMesh}?}
